### 2020-01-27 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
a lot of minor corrections

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{academicons}
%\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Optimization Letters}
%
\begin{document}

\title{A Computationally Efficient Approach for Solving Lexicographic Multicriteria Optimization Problems\thanks{This research was supported by the Russian Science Foundation, project No 16-11-10150 ``Novel efficient methods and software tools for time-consuming decision making problems using supercomputers of superior performance.''}
}

@@

\institute{               
V. Gergel \at
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
\email{gergel@unn.ru} 
\and
E. Kozinov \at
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
\email{evgeny.kozinov@itmm.unn.ru} 
\and
K. Barkalov \at
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
\email{barkalov@vmk.unn.ru}
}

@@

\begin{abstract}
This paper proposes a computationally efficient approach for solving complex lexicographic multicriteria optimization problems in which efficiency criteria can be multiextremal and computing the values of criteria can be time-consuming. It is also assumed that in the course of calculations, how problems are formulated may change and consequently, solving dynamically defined sets of multicriteria optimization problems may become necessary. The proposed approach is based on reducing multidimensional problems to one-dimensional global optimization problems, utilizing efficient global search algorithms, and reusing the search information obtained in the process of calculations. Results of computational experiments demonstrate that the proposed approach can significantly reduce the computational complexity of solving multicriteria optimization problems.
\keywords{Multicriteria optimization \and Lexicographic ordering \and Global optimization \and Dimensional reduction \and Search information \and Computational complexity}
\end{abstract}

@@

The multicriteria (or vector) optimization (MCO) problem can be defined as follows:
\begin{equation}\label{eq:1}
f(y) = (f_1(y), f_2(y), \dots , f_s(y)) \to min,  y \in D,
\end{equation}
where $f(y) = (f_1(y), f_2(y), \dots , f_s(y))$ is the vector efficiency criterion, $y = (y_1, y_2, \dots , y_N)$ is the vector of variable parameters, and $N$ is the dimension of the multicriteria optimization problem to be solved. The search domain $D$ defines the set of possible parameter values and is usually an $N$-dimensional hypercube
\begin{equation}\label{eq:2}
D  = \{ y\in R^N: a_i \leq y_i \leq b_i, 1 \leq i \leq N \}
\end{equation}
for the given boundary vectors $a$ and $b$.

Without a loss of generality, it is assumed that the values of the efficiency criteria are not negative and their decrease corresponds to an increase in the effectiveness of the considered decisions $y \in D$. Problem (\ref{eq:1}) is considered in relation to the most difficult decision-making problems in which the efficiency criteria $f_i(y)$, $1 \leq i \leq s$, can be significantly multiextremal, and the procedures for calculating the values of efficiency criteria at points of the search domain $y \in D$ can be computationally expensive. It is also assumed that the criteria $f_i(y)$, $1 \leq i \leq s$, satisfy the Lipschitz condition
\begin{equation}\label{eq:2l}
|f_i (y')-f_i (y'')| \leq L_i \|y'-y''\|, y',y''\in D, 1 \leq i \leq s
\end{equation}
where $L_i$ is the Lipschitz constants for the function $f_i(y)$, $1 \leq i \leq s$, and $\|*\|$ denotes the Euclidean norm in $R^N$. Fulfillment of the Lipschitz condition means that for small variations of the decision $y \in D$, corresponding changes in the values of the criteria $f_i(y)$, $1 \leq i \leq s$, are limited.

@@

This approach is also widely known as the method of successive concessions (MSC) \cite{c3,c4,c5}. The choice of feasible concessions $\delta_i$, $1 \leq i < s$ in the computational scheme (\ref{eq:7}) allows one to obtain any efficient decision $\widetilde{y}^* \in P_{lex}(f,D)$ and take into account the peculiarities of the MCOlex problem being solved. At the same time, this approach makes it necessary, at each stage of scheme (\ref{eq:7}), to solve more complex global optimization problems with nonlinear constraints.

@@

The extended formulation of lexicographic multicriteria optimization problems (\ref{eq:7})-(\ref{eq:8}) involves multiple solutions of multiextremal optimization problems with nonlinear constraints. Problems of this type are computationally time-consuming and subject to the ``curse of dimensionality'' -- computational complexity increases exponentially with increasing dimensionality. The proposed approach for solving such problems is based on three key ideas:
\begin{itemize}
  \item Reduction of multidimensional problems of multiextremal optimization to problems of one-dimensional global search by using mappings based on Peano curves;
  \item Using the index method of global optimization, which allows solving optimization problems with constraints without using penalty functions;
  \item Repeated use of search information obtained in the process of computing, for solving multiple global optimization problems.
\end{itemize}

@@

Adaptive selection of points $y^{k+1} \in D$ at the iterations of the global search involves the analysis of volumetric multidimensional search information $\omega_k (k \gg 1)$, which determines the high computational complexity of the decisive rules $G_k$,$k=1,2,\dots$ of global search algorithms. This computational complexity can be significantly simplified by reducing the optimization problems to be solved using Peano \textit{space-filling curves} or \textit{evolvents} $y(x)$, that uniquely and continuously map the interval $[0,1]$ to an $N$-dimensional hypercube D (see, e.g., \cite{c17,c18,c23}). As a result of this reduction, the initial multidimensional multicriteria optimization problem (\ref{eq:5}) is reduced to a one-dimensional problem:
\begin{equation}\label{eq:10}
f(y(x)) = (f_1(y(x)), f_2(y(x)), \dots , f_s(y)(x)) \to min_{leq},  x \in [0,1].
\end{equation}

It should be noted that the one-dimensional functions obtained as a result of the reduction satisfy the uniform H\"older condition (see \cite{c17,c18}), that is
\begin{equation}\label{eq:11}
|f_i (y(x'))-f_i (y(x';))| \leq H_i \|x'-x''\|, x',x''\in [0,1], 1 \leq i \leq s,
\end{equation}
where the constants $H_i$ are determined by the ratio $H_i=2L_i\sqrt{N+3}$, $1 \leq i \leq m$, $L_i$ are the Lipschitz constants from (\ref{eq:2l}), and $N$ is the dimension of the optimization problem (\ref{eq:1}).

Using dimension reduction the search information $\omega_k$ can be converted from (\ref{eq:9}) to the form
\begin{equation}\label{eq:12}
A_k=\{(x_i, y(x_i), f_i=f(y(x_i)): 1 \leq i \leq k \},
\end{equation}
in which, in addition to the reduced representation, the data is arranged in ascending order\footnote{Data ordering is reflected by using a subscript.} of points $x_i$, $1 \leq i \leq k$, that is
\begin{equation}
x_1 < x_2 < \dots < x_k	
\end{equation}
for a more efficient execution of global search algorithms.

@@

The problems solved in the framework of the computational scheme (\ref{eq:7}) are one-dimensional global optimization problems with nonlinear constraints
\begin{equation}\label{eq:13}
\min{\{\varphi(x):g_i(x)\leq 0, 1 \leq i \leq m, x\in \Delta=[0,1]\}}
\end{equation}
(the notation $g_{m+1}(x) = \varphi(x)$ will also be used later).

The presence of nonlinear constraints significantly complicates the complexity of solving global optimization problems; the resulting solutions must belont to a feasible domain
\begin{equation}\label{eq:14}
\Delta_g  = \{ x\in \Delta=[0,1]:g_i(x)\leq 0,   1 \leq i \leq m \}.
\end{equation}

@@

The function $F(x)$ consists of separate fragments of the constraints $g_i(x) \leq 0$, $1 \leq i \leq m$, and the minimized function $\varphi(x)$. For the homogeneity of the components, the function $F(x)$ is then converted to the form 
\begin{equation}\label{eq:17}
\Phi (x) = 
 \begin{cases}
   g_\nu(x) / H_\nu, & \nu < M, \\
   (g_M(x)-z^*_M) / H_M, & \nu = M,
 \end{cases}
\end{equation}
where $M$ is the constraint number for which there are no feasible points (the maximum value of the index is $\nu(x)$), $z^*_M$ is the value of the minimum constraint violation $g_M(x)$\footnote{If $M=m+1$, then $z_M^*$ is the minimum value of the function $\varphi(x)$.}, and $H_\nu$, $1\leq \nu \leq M$, are the H\"older constants from (\ref{eq:11}). As a rule, these values are a priori unknown, but when performing calculations, instead of these values, their adaptive estimates obtained in the process of calculations can be applied. For this, the search information $A_k$ from (\ref{eq:12}) should be expanded with data
\begin{equation}\label{eq:18}
A_k=\{(x_i, z_i, \nu_i, y(x_i), f_i=f( y(x_i)): 1 \leq i \leq k \},
\end{equation}
where $z_i= \Phi(x_i)$, $1 \leq i \leq k$. Then estimates of the required values can be determined as follows
\begin{equation}\label{eq:19}
M^k= \max{\{\nu=\nu(x_i), 1\leq i \leq k \}},
\end{equation}

@@

The first trial is carried out at an arbitrary internal point $x^1\in (0,1)$. The calculation results are constantly added to the set $A_k$ from (\ref{eq:12}); in addition, into $A_k$ are also added the points $x_0=0$ and $x_{k+1}=1$ (the values $z_0$ and $z_{k+1}$ are not defined and not used) for the convenience of subsequent formulations. The choice of the point $x^{k+1}$, $k\geq 1$ of any next trial is determined by the following rules.

@@

Results of using the AGCS algorithm to solve the test problem from Fig. \ref{fig:1} with the parameters $r_1=r_2=r_3=2$ and $\varepsilon=10^5$are shown in Fig. \ref{fig:2}.  The coordinates of the trial points performed by the algorithm in the process of solving the problem are marked in Fig. \ref{fig:1} by three rows of vertical strokes. The strokes in the upper row correspond to points with a unit index, the second row to points whose indices equal to 2; the points marked with strokes in the bottom row belong to the feasible domain. The coordinates of trials performed at close points are marked with a dark rectangle. In total, the value of the first constraint was computed 147 times, the value of the second constraint -- 84 times, and the value of the minimized function was calculated only 35 times.

@@

Moreover, using search information $A_k$ allows to reduce the multistage solution of the MCO problem in accordance with the scheme (\ref{eq:7}) to the solution of the only global optimization problem in the last stage of the scheme (\ref{eq:7}), namely 
\begin{equation}\label{eq:26}
P_{\delta lex} (f,\delta,D)=Arg \min_{y\in D}{f_s(y)}, f_j(y)\leq f_j^*+\delta_j, 1 \leq j < s,
\end{equation}
where for the unknown a priori values $f_j^*$, $1 \leq j < s$, can be used the estimates $z_j^k$, $1 \leq j < s$, from (\ref{eq:20}) obtained from the search information $A_k$,  and for the constants $\delta_j$, $1 \leq j<s$, we can use the values normalized to the range of constraints values, that is
\begin{equation}\label{eq:27}
	\begin{matrix}
	\delta_j=z_j^k+\theta_j (g_j^k-z_j^k ), 0\leq \theta_j\leq 1,1\leq j < s,\\
	g_j^k= \max{\{ g_j (x_i ) : \nu(x_i)=j,1\leq i\leq k \}}.
	\end{matrix}
\end{equation}

The applicability of such a one-step scheme (\ref{eq:26})-(\ref{eq:27}) instead of the scheme (\ref{eq:7}) is computationally evaluated in Section \ref{sec:4}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
%\usepackage{academicons}
%\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Optimization Letters}
%
\begin{document}

\title{A Computationally Efficient Approach for Solving Lexicographic Multicriteria Optimization Problems\thanks{This research was supported by the Russian Science Foundation, project No 16-11-10150 ``Novel efficient methods and software tools for time-consuming decision making problems using supercomputers of superior performance''.}
}

@@

\institute{               
V. Gergel \at
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
\email{gergel@unn.ru} 
\and
E. Kozinov \at
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
\email{evgeny.kozinov@itmm.unn.ru} 
\and
K. Barkalov \at
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
\email{konstantin.barkalov@itmm.unn.ru}
}

@@

\begin{abstract}
This paper proposes a computationally efficient approach for solving complex lexicographic multicriteria optimization problems in which efficiency criteria can be multiextremal and computing the values of criteria can be time-consuming. It is also assumed that in the course of calculations, how problems are formulated may change and consequently, solving dynamically defined sets of multicriteria optimization problems may become necessary. The proposed approach is based on reducing multidimensional problems to one-dimensional global optimization problems, utilizing efficient global search algorithms, and reusing the search information obtained in the process of calculations. Results of computational experiments demonstrate that the proposed approach can significantly reduce the computational complexity of solving multicriteria optimization problems.
\keywords{Multicriteria optimization \and Lexicographic ordering \and Global optimization \and Dimensionality reduction \and Search information \and Computational complexity}
\end{abstract}

@@

The multicriteria (or vector) optimization (MCO) problem can be defined as follows:
\begin{equation}\label{eq:1}
f(y) = (f_1(y), f_2(y), \dots , f_s(y)) \to min, \; y \in D,
\end{equation}
where $f(y) = (f_1(y), f_2(y), \dots , f_s(y))$ is the vector efficiency criterion, $y = (y_1, y_2, \dots , y_N)$ is the vector of variable parameters, and $N$ is the dimension of the multicriteria optimization problem to be solved. The search domain $D$ defines the set of possible parameter values and is usually an $N$-dimensional hypercube
\begin{equation}\label{eq:2}
D  = \{ y\in R^N: a_i \leq y_i \leq b_i, \; 1 \leq i \leq N \}
\end{equation}
for the given boundary vectors $a$ and $b$.

Without a loss of generality, it is assumed that the values of the efficiency criteria are not negative and their decrease corresponds to an increase in the effectiveness of the considered decisions $y \in D$. Problem (\ref{eq:1}) is considered in relation to the most difficult decision-making problems in which the efficiency criteria $f_i(y)$, $1 \leq i \leq s$, can be significantly multiextremal, and the procedures for calculating the values of efficiency criteria at points of the search domain $y \in D$ can be computationally expensive. It is also assumed that the criteria $f_i(y)$, $1 \leq i \leq s$, satisfy the Lipschitz condition
\begin{equation}\label{eq:2l}
|f_i (y')-f_i (y'')| \leq L_i \|y'-y''\|, \; y',y''\in D,\; 1 \leq i \leq s,
\end{equation}
where $L_i$ is the Lipschitz constants for the function $f_i(y)$, $1 \leq i \leq s$, and $\|*\|$ denotes the Euclidean norm in $R^N$. Fulfillment of the Lipschitz condition means that for small variations of the decision $y \in D$, corresponding changes in the values of the criteria $f_i(y)$, $1 \leq i \leq s$, are limited.

@@

This approach is also widely known as the method of successive concessions (MSC) \cite{c3,c4,c5}. The choice of feasible concessions $\delta_i$, $1 \leq i < s$, in the computational scheme (\ref{eq:7}) allows one to obtain any efficient decision $\widetilde{y}^* \in P_{lex}(f,D)$ and take into account the peculiarities of the MCOlex problem being solved. At the same time, this approach makes it necessary, at each stage of scheme (\ref{eq:7}), to solve more complex global optimization problems with nonlinear constraints.

@@

The extended formulation of lexicographic multicriteria optimization problems (\ref{eq:7})--(\ref{eq:8}) involves multiple solutions of multiextremal optimization problems with nonlinear constraints. Problems of this type are computationally time-consuming and subject to the ``curse of dimensionality'' -- computational complexity increases exponentially with increasing dimensionality. The proposed approach for solving such problems is based on three key ideas:
\begin{itemize}
  \item Reduction of multidimensional problems of multiextremal optimization to problems of one-dimensional global search by using mappings based on Peano curves;
  \item Using the index method of global optimization, which allows solving optimization problems with constraints without using penalty functions;
  \item Repeated use of search information obtained in the process of computing, for solving multiple global optimization problems.
\end{itemize}

@@

Adaptive selection of points $y^{k+1} \in D$ at the iterations of the global search involves the analysis of volumetric multidimensional search information $\omega_k$ $(k \gg 1)$, which determines the high computational complexity of the decisive rules $G_k$, $k=1,2,\dots$ of global search algorithms. This computational complexity can be significantly simplified by reducing the optimization problems to be solved using Peano \textit{space-filling curves} or \textit{evolvents} $y(x)$, that uniquely and continuously map the interval $[0,1]$ to an $N$-dimensional hypercube $D$ (see, e.g., \cite{c17,c18,c23}). As a result of this reduction, the initial multidimensional multicriteria optimization problem (\ref{eq:5}) is reduced to a one-dimensional problem:
\begin{equation}\label{eq:10}
f(y(x)) = (f_1(y(x)), f_2(y(x)), \dots , f_s(y(x)) \to min_{leq},  x \in [0,1].
\end{equation}

It should be noted that the one-dimensional functions obtained as a result of the reduction satisfy the uniform H\"older condition (see \cite{c17,c18}), that is
\begin{equation}\label{eq:11}
|f_i (y(x'))-f_i (y(x''))| \leq H_i \|x'-x''\|, \; x',x''\in [0,1],\; 1 \leq i \leq s,
\end{equation}
where the constants $H_i$ are determined by the ratio $H_i=2L_i\sqrt{N+3}$, $1 \leq i \leq m$, $L_i$ are the Lipschitz constants from (\ref{eq:2l}), and $N$ is the dimension of the optimization problem (\ref{eq:1}).

Using dimension reduction the search information $\omega_k$ can be converted from (\ref{eq:9}) to the form
\begin{equation}\label{eq:12}
A_k=\{(x_i, y(x_i), f_i=f(y(x_i))): 1 \leq i \leq k \},
\end{equation}
in which, in addition to the reduced representation, the data is arranged in ascending order\footnote{Data ordering is reflected by using a subscript.} of points $x_i$, $1 \leq i \leq k$, that is
\begin{equation}
x_1 < x_2 < \dots < x_k	
\end{equation}
for a more efficient execution of global search algorithms.

@@

The problems solved in the framework of the computational scheme (\ref{eq:7}) are one-dimensional global optimization problems with nonlinear constraints
\begin{equation}\label{eq:13}
\min{\{\varphi(x):g_i(x)\leq 0, \; 1 \leq i \leq m,\; x\in \Delta=[0,1]\}}
\end{equation}
(the notation $g_{m+1}(x) = \varphi(x)$ will also be used later).

The presence of nonlinear constraints significantly complicates the complexity of solving global optimization problems; the resulting solutions must belong to a feasible domain
\begin{equation}\label{eq:14}
\Delta_g  = \{ x\in \Delta=[0,1]:g_i(x)\leq 0,   1 \leq i \leq m \}.
\end{equation}

@@

The function $F(x)$ consists of separate fragments of the constraints $g_i(x) \leq 0$, $1 \leq i \leq m$, and the minimized function $\varphi(x)$. For the homogeneity of the components, the function $F(x)$ is then converted to the form 
\begin{equation}\label{eq:17}
\Phi (x) = 
 \begin{cases}
   g_\nu(x) / H_\nu, & \nu < M, \\
   (g_M(x)-z^*_M) / H_M, & \nu = M,
 \end{cases}
\end{equation}
where $M$ is the constraint number for which there are no feasible points (the maximum value of the index is $\nu(x)$), $z^*_M$ is the value of the minimum constraint violation $g_M(x)$\footnote{If $M=m+1$, then $z_M^*$ is the minimum value of the function $\varphi(x)$.}, and $H_\nu$, $1\leq \nu \leq M$, are the H\"older constants from (\ref{eq:11}). As a rule, these values are a priori unknown, but when performing calculations, instead of these values, their adaptive estimates obtained in the process of calculations can be applied. For this, the search information $A_k$ from (\ref{eq:12}) should be expanded with data
\begin{equation}\label{eq:18}
A_k=\{(x_i, z_i, \nu_i, y(x_i), f_i=f( y(x_i))): 1 \leq i \leq k \},
\end{equation}
where $z_i= \Phi(x_i)$, $1 \leq i \leq k$. Then estimates of the required values can be determined as follows
\begin{equation}\label{eq:19}
M^k= \max{\{\nu=\nu(x_i), 1\leq i \leq k \}},
\end{equation}

@@

The first trial is carried out at an arbitrary internal point $x^1\in (0,1)$. The calculation results are constantly added to the set $A_k$ from (\ref{eq:12}); in addition, into $A_k$ are also added the points $x_0=0$ and $x_{k+1}=1$ (the values $z_0$ and $z_{k+1}$ are not defined and not used) for the convenience of subsequent formulations. The choice of the point $x^{k+1}$, $k\geq 1$, of any next trial is determined by the following rules.

@@

Results of using the AGCS algorithm to solve the test problem from Fig.~\ref{fig:1} with the parameters $r_1=r_2=r_3=2$ and $\varepsilon=10^{-5}$ are shown in Fig. \ref{fig:2}.  The coordinates of the trial points performed by the algorithm in the process of solving the problem are marked in Fig. \ref{fig:1} by three rows of vertical strokes. The strokes in the upper row correspond to points with a unit index, the second row to points whose indices equal to 2; the points marked with strokes in the bottom row belong to the feasible domain. The coordinates of trials performed at close points are marked with a dark rectangle. In total, the value of the first constraint was computed 147 times, the value of the second constraint -- 84 times, and the value of the minimized function was calculated only 35 times.

@@

Moreover, using search information $A_k$ allows to reduce the multistage solution of the MCO problem in accordance with the scheme (\ref{eq:7}) to the solution of the only global optimization problem in the last stage of the scheme (\ref{eq:7}), namely 
\begin{equation}\label{eq:26}
P_{\delta lex} (f,\delta,D)=Arg \min_{y\in D}{f_s(y)}, f_j(y)\leq f_j^*+\delta_j, 1 \leq j < s,
\end{equation}
where for the unknown a priori values $f_j^*$, $1 \leq j < s$, can be used the estimates $z_j^k$, $1 \leq j < s$, from (\ref{eq:20}) obtained from the search information $A_k$,  and for the constants $\delta_j$, $1 \leq j<s$, we can use the values normalized to the range of constraints values, that is
\begin{equation}\label{eq:27}
	\begin{matrix}
	\delta_j=z_j^k+\theta_j (g_j^k-z_j^k ),\; 0\leq \theta_j\leq 1, \; 1 \leq j < s,\\
	g_j^k= \max{\{ g_j (x_i ) : \nu(x_i)=j,\; 1\leq i\leq k \}}.
	\end{matrix}
\end{equation}

The applicability of such a one-step scheme (\ref{eq:26})--(\ref{eq:27}) instead of the scheme (\ref{eq:7}) is computationally evaluated in Section \ref{sec:4}.
